Practical Optional Types for Clojure

### 2015-02-24 intro.tex
Improvements to start of 2.

The popularity of dynamically-typed languages languages in software
development, combined with a recognition that types often improve
programmer productivity, software reliability, and performance, has
led to the recent development of a wide variety of optional and
gradual type systems aimed at checking existing programs written in
existing languages.  These include Microsoft's TypeScript for
JavaScript, Facebook's Hack for PHP and Flow for JavaScript, and MyPy
for Python among the optional systems, and Typed Racket, Reticulated
Python, and GradualTalk among gradually-typed system.\footnote{We
  reserve the term ``gradual typing'' for systems which soundly
  interoperate between typed and untyped code; systems which do not
  enforce type invariants we describe as ``optionally typed''.}
%FIXME: add citations for all those systems.

>>>>

The popularity of dynamically-typed languages languages in software
development, combined with a recognition that types often improve
programmer productivity, software reliability, and performance, has
led to the recent development of a wide variety of optional and
gradual type systems aimed at checking existing programs written in
existing languages.  These include Microsoft's TypeScript for
JavaScript, Facebook's Hack for PHP and Flow for JavaScript, and MyPy
for Python among the optional systems, and Typed Racket, Reticulated
Python, and GradualTalk among gradually-typed system.\footnote{We
  reserve the term ``gradual typing'' for systems such as Typed Racket which soundly
  interoperate between typed and untyped code; systems like Typed Clojure or TypeScript which do not
  enforce type invariants we describe as ``optionally typed''.}
%FIXME: add citations for all those systems.

### 2015-02-24 overview.tex
Improvements to start of 2.

@@

>>>>

\label{sec:overview}

We now begin a tour of the central features of Typed Clojure,
beginning with Clojure itself. In our presentation, we will make 
use of the full Typed Clojure system to illustrate the key type system
ideas, before studying the key features in detail in
section~\ref{sec:formal}.

@@

Clojure~\cite{something-for-clojure} is a Lisp built to run on the
Java Virtual Machine with exemplary support for concurrent programming
and immutable data structures. It emphaisizes mostly-functional
programming, restricting imperative updates to a limited set of
structures which have specific thread synchronization behavior. By
default, it provides fast implemenations of immutable lists, vectors,
and hash tables, which are used for most data structures, although it
also provides means for defining new records.

One of Clojure's primary advantages is easy interoperation with
existing Java libraries. It automatically generates appropriate JVM
bytecode to make Java method and constructor calls, and treats Java
values as any other Clojure value. However, this smooth
interoperability comes at the cost of pervasive \clj{null}, which
leads to the possibility of null pointer exceptions---a drawback we
address in Typed Clojure.
